---
title: "FARL: Use Factor-Augmented Regularized Latent Regression for Large-Scale Assessment"
output:
  rmarkdown::html_vignette:
    toc: true
link-citations: true
vignette: >
  %\VignetteIndexEntry{FARL: Use Factor-Augmented Regularized Latent Regression for Large-Scale Assessment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!-- Run knitr::knit("FARL.Rmd.orig", output = "FARL.Rmd") to prebuild the vignette -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Introduction

The `FARL` package implements factor-augmented regularized latent regression
(FARLR) for large-scale assessments. FARLR is designed for latent regression
with high-dimensional, strongly dependent background variables. It decomposes
their variation into common latent factors and idiosyncratic components,
includes both components in the latent regression, and uses sparse
regularization to select a parsimonious set of relevant covariates. This
structure improves numerical stability while retaining interpretable
background variables and supporting plausible-value generation for
group-level inference.

The current package provides a unified fitting interface for the FARLR and
FARLR-Debias estimators described in the accompanying paper. It supports
dichotomous 2PL and 3PL items, three-category generalized partial credit model
(GPCM) items, high-dimensional covariates, and plausible-value generation.

The development version can be installed with

```{r installation}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("MAP-LAB-UW/FARL", build_vignettes = TRUE)
torch::install_torch()
```

```{r load-package}
library(FARL)
```

`Farlr_mml()` is the public interface for both FARLR estimators. The option
`method = "FARLR_EMM"` implements FARLR through an importance-sampling-based
expectation-maximization-maximization algorithm, whereas
`method = "FARLR_Debias"` applies a bias correction to the regularized
coefficients. `Dire_mml()` provides a PCA-based latent regression comparison.

# Data Input

Data required for the analyses are summarized below.

| Analysis | Item Responses | Item Parameters | Background Covariates | Main Covariates | Formula |
| :-: | :-: | :-: | :-: | :-: | :-: |
| `Farlr_mml(..., method = "FARLR_EMM")` | $\checkmark$ | $\checkmark$ | $\checkmark$ | $\checkmark$ | |
| `Farlr_mml(..., method = "FARLR_Debias")` | $\checkmark$ | $\checkmark$ | $\checkmark$ | $\checkmark$ | |
| `Dire_mml()` | $\checkmark$ | $\checkmark$ | $\checkmark$ | $\checkmark$ | $\checkmark$ |

Here we first use `sim_a1`, a simulated dataset for one-dimensional 2PL
analysis. It contains $N=3000$ respondents, $J=10$ items, and $P=60$
background covariates.

## Item responses

Item responses should be an $N$ by $J$ numeric matrix. Dichotomous responses
are coded as 0 or 1, and missing responses may be coded as `NA`.

```{r sim-a1-response}
data(sim_a1)

dim(sim_a1$Y)
# [1] 3000   10
head(sim_a1$Y)
#      i001 i002 i003 i004 i005 i006 i007 i008 i009 i010
# [1,]    1    1    1    1    1    1    0    1    1    1
# [2,]    0    0    1    0    1    0    0    1    1    0
# [3,]    1    1    1    0    0    0    0    0    1    0
# [4,]    0    0    1    0    1    0    0    0    0    0
# [5,]    1    0    1    0    1    1    0    1    0    0
# [6,]    0    0    1    0    1    1    0    1    1    0
```

## Background covariates

Background covariates should be an $N$ by $P$ numeric matrix. Covariates may
be binary or continuous, but each column must have positive variance.

```{r sim-a1-covariates}
dim(sim_a1$X)
# [1] 3000   60
head(sim_a1$X[, 1:10])
#      [,1] [,2]       [,3] [,4] [,5] [,6] [,7]       [,8] [,9]      [,10]
# [1,]    1    1  2.0679032    1    1    1    1  1.3037993    1 1.09682610
# [2,]    1    0  0.1913680    0    1    1    0  0.2450981    1 0.63345311
# [3,]    1    1  0.9718647    1    1    1    1  0.1302181    0 0.36494637
# [4,]    0    0 -0.4845058    1    0    0    0  0.1197165    0 0.21706507
# [5,]    1    1  0.8427349    1    1    1    0  0.1999399    1 0.47819559
# [6,]    0    1  0.2229768    1    1    1    1 -0.4628130    1 0.04376757
```

The `main` argument contains the column indices of primary covariates. These
variables are not penalized in the regularized regression. In this example,
the five main covariates are

```{r main-covariates}
main <- c(1, 2, 15, 29, 45)
```

## Item parameters

The item parameter table must follow the same item order as the columns of the
response matrix. For a 2PL item, `a` is the discrimination, `b` is the
difficulty, and `c` is zero.

```{r sim-a1-parameters}
sim_a1$parTab

# 1	-0.1280856	1.0005257	0	item1	comp	main	1.0005257	-0.1280856	
# 2	0.4959430	1.1258010	0	item2	comp	main	1.1258010	0.4959430	
# 3	-0.8648743	0.8435464	0	item3	comp	main	0.8435464	-0.8648743	
# 4	0.6850886	1.8747028	0	item4	comp	main	1.8747028	0.6850886	
# 5	-1.4793505	0.8534336	0	item5	comp	main	0.8534336	-1.4793505	
# 6	-0.3336796	1.0371741	0	item6	comp	main	1.0371741	-0.3336796	
# 7	1.8529386	1.4060425	0	item7	comp	main	1.4060425	1.8529386	
# 8	-0.4022468	1.4886061	0	item8	comp	main	1.4886061	-0.4022468	
# 9	0.3655995	1.0044162	0	item9	comp	main	1.0044162	0.3655995	
# 10	0.6513511	1.2750785	0	item10	comp	main	1.2750785	0.6513511	
```

<!-- BEGIN: paste sim_a1 output here -->

```text
# Paste the printed sim_a1 dimensions, response rows, covariate rows,
# and parameter table here.
```

<!-- END: paste sim_a1 output here -->

## `sim_a2`: mixed 3PL and GPCM responses

The package also includes `sim_a2`, which contains mixed 3PL and GPCM items.
For a 3PL item, `c` is the lower asymptote. A GPCM item is identified by finite
`b1` and `b2` step parameters.

```{r sim-a2-input}
data(sim_a2)

dim(sim_a2$X)
# [1] 3000   60
dim(sim_a2$Y)
# [1] 3000   10
table(sim_a2$itemtype)
#  3PL gpcm 
#   5    5 
head(sim_a2$Y)
#      i001 i002 i003 i004 i005 i006 i007 i008 i009 i010
# [1,]    1    2    1    2    1    1    1    2    1    1
# [2,]    0    1    0    2    1    2    0    2    1    1
# [3,]    1    0    1    2    1    1    0    0    1    2
# [4,]    0    0    0    2    1    1    0    0    1    0
# [5,]    1    1    1    1    1    0    0    1    1    0
# [6,]    1    1    1    2    1    0    0    2    1    0

sim_a2$parTab[, c("ItemID", "itemtype", "a", "b", "c", "b1", "b2")]
# item1	3PL	1.0005257	-0.1280856	0.1624870	NA	NA
# item2	gpcm	1.1258010	NA	0.0000000	-0.3738297	0.6175084
# item3	3PL	0.8435464	0.4959430	0.2444852	NA	NA
# item4	gpcm	1.8747028	NA	0.0000000	-1.4734702	-0.3204836
# item5	3PL	0.8534336	-0.8648743	0.1599157	NA	NA
# item6	gpcm	1.0371741	NA	0.0000000	0.1658423	1.0450782
# item7	3PL	1.4060425	0.6850886	0.1887100	NA	NA
# item8	gpcm	1.4886061	NA	0.0000000	-0.7241589	0.4505988
# item9	3PL	1.0044162	-1.4793505	0.1994257	NA	NA
# item10	gpcm	1.2750785	NA	0.0000000	-0.2383690	0.8670740
```

<!-- BEGIN: paste sim_a2 output here -->

```text
# Paste the sim_a2 item-type table and mixed-item parameter table here.
```

<!-- END: paste sim_a2 output here -->

# Data Output

The main model and plausible-value functions return the following objects.

| Function | Main output |
| :-: | :-- |
| `Farlr_mml()` | Regression coefficients, residual standard deviation, selected tuning parameter, factor scores, and method-specific design matrices |
| `Farlr_drawPVs()` | Plausible values, EAP estimates, posterior variances, posterior modes, and prior means |
| `Dire_mml()` | A fitted `mmlMeans` object with DIRE coefficients and the residual-PCA object |
| `Dire_drawPVs()` | A data frame containing respondent IDs and plausible values |

# Factor-Augmented Regularized Latent Regression

`Farlr_mml()` is the unified interface for the two FARLR estimators. In both
methods, estimated factors capture shared dependence among covariates, while
regularization identifies a sparse set of relevant idiosyncratic predictors.
Variables listed in `main` remain unpenalized so that key reporting variables
are retained in the population model.

| Method | Description |
| :-: | :-- |
| `FARLR_EMM` | Importance-sampling E-step, regularized variable-selection M-step, and an additional unpenalized M-step for the active coefficients |
| `FARLR_Debias` | Regularized estimation using factors and idiosyncratic components, followed by correction of LASSO shrinkage bias |

When `K_hat` is not supplied, the number of factors is estimated by parallel
analysis. If the number of factors is known, supplying `K_hat` avoids this
additional step.

## FARLR via ISEMM

This method combines the estimated factor scores and observed covariates in the
latent regression. At each iteration, importance sampling approximates the
posterior expectations of latent proficiency, a LASSO update selects relevant
covariates, and a second unpenalized M-step refines the active coefficients.

```{r farlr-emm}
mmlcomp_emm <- with(
  sim_a1,
  Farlr_mml(
    X = X,
    Y = Y,
    parTab = parTab,
    method = "FARLR_EMM",
    main = main,
    seed = 2026
  )
)
#  |++++++++++++++++++++++++++++++++++++++++++++++++++| 100% elapsed=00s  
#  |=======================================================================| 100%

round(mmlcomp_emm$coefficients, 3)
 #   FS1    FS2    FS3    FS4     X1     X2     X3     X4     X5     X6     X7 
 # 0.360 -0.051  0.089  0.163  0.146  0.139  0.000  0.000  0.000  0.000  0.000 
 #    X8     X9    X10    X11    X12    X13    X14    X15    X16    X17    X18 
 # 0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.142  0.000  0.000  0.000 
 #   X19    X20    X21    X22    X23    X24    X25    X26    X27    X28    X29 
 # 0.247  0.000  0.000  0.152  0.000  0.000  0.000  0.000  0.000  0.000  0.108 
 #   X30    X31    X32    X33    X34    X35    X36    X37    X38    X39    X40 
 # 0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000 
 #   X41    X42    X43    X44    X45    X46    X47    X48    X49    X50    X51 
 # 0.000  0.000  0.000  0.000  0.163  0.000  0.000  0.000  0.000  0.000  0.000 
 #   X52    X53    X54    X55    X56    X57    X58    X59    X60 
 # 0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000 

round(mmlcomp_emm$sigma, 3)
# [1] 0.702
```

## FARLR Debias

The debias method separates the common factor structure from the idiosyncratic
component of each covariate. It first obtains regularized coefficient estimates
and then corrects part of the LASSO shrinkage bias. This decorrelated
parameterization is intended to stabilize selection when background variables
are strongly dependent.

```{r farlr-debias}
mmlcomp_debias <- with(
  sim_a1,
  Farlr_mml(
    X = X,
    Y = Y,
    parTab = parTab,
    method = "FARLR_Debias",
    main = main,
    seed = 2026
  )
)
#  |++++++++++++++++++++++++++++++++++++++++++++++++++| 100% elapsed=00s  
#  |=======================================================================| 100%

round(mmlcomp_debias$coefficients, 3)
 #   FS1    FS2    FS3    FS4     X1     X2     X3     X4     X5     X6     X7 
 # 0.025 -0.665  0.020  0.047  0.147  0.125  0.000  0.000  0.000  0.000  0.000 
 #    X8     X9    X10    X11    X12    X13    X14    X15    X16    X17    X18 
 # 0.000  0.000  0.000  0.360  0.000  0.000  0.000  0.127  0.000  0.000  0.000 
 #   X19    X20    X21    X22    X23    X24    X25    X26    X27    X28    X29 
 # 0.243  0.129  0.000  0.148  0.000  0.000  0.000  0.129  0.000  0.000  0.108 
 #   X30    X31    X32    X33    X34    X35    X36    X37    X38    X39    X40 
 # 0.000  0.000  0.437  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000 
 #   X41    X42    X43    X44    X45    X46    X47    X48    X49    X50    X51 
 # 0.523  0.000  0.000  0.000  0.157  0.000  0.000  0.000  0.000  0.000  0.000 
 #   X52    X53    X54    X55    X56    X57    X58    X59    X60 
 # 0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000 

round(mmlcomp_debias$sigma, 3)
# [1] 0.631
```

## Mixed 3PL and GPCM items

The same interface can analyze the mixed-format responses in `sim_a2`.
`Farlr_mml()` determines item types from `parTab`: finite `b1` and `b2`
identify GPCM items, and a nonzero `c` identifies 3PL items.

```{r farlr-mixed}
mmlcomp_mixed <- with(
  sim_a2,
  Farlr_mml(
    X = X,
    Y = Y,
    parTab = parTab,
    method = "FARLR_Debias",
    main = main,
    seed = 2026
  )
)
#  |++++++++++++++++++++++++++++++++++++++++++++++++++| 100% elapsed=00s  
#  |=======================================================================| 100%
 
round(mmlcomp_mixed$coefficients,3)
#  FS1    FS2    FS3    FS4     X1     X2     X3     X4     X5     X6     X7 
# 0.025 -0.665 -0.006  0.054  0.126  0.109  0.000  0.000  0.000  0.000  0.000 
#    X8     X9    X10    X11    X12    X13    X14    X15    X16    X17    X18 
# 0.000  0.000  0.000  0.445  0.000  0.000  0.000  0.090  0.000  0.000  0.000 
#   X19    X20    X21    X22    X23    X24    X25    X26    X27    X28    X29 
# 0.250  0.134  0.000  0.149  0.000  0.000  0.000  0.152  0.000  0.000  0.133 
#   X30    X31    X32    X33    X34    X35    X36    X37    X38    X39    X40 
# 0.000  0.000  0.429  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000 
#   X41    X42    X43    X44    X45    X46    X47    X48    X49    X50    X51 
# 0.534  0.000  0.000  0.000  0.162  0.000  0.000  0.000  0.000  0.000  0.000 
#   X52    X53    X54    X55    X56    X57    X58    X59    X60 
# 0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000  0.000 
 
round(mmlcomp_mixed$sigma, 3)
# [1] 0.594
```
# Plausible Values for FARLR

`Farlr_drawPVs()` combines the fitted FARLR latent-regression prior with each respondent's item-response likelihood. For each respondent, the function evaluates the posterior distribution over a set of quadrature points and computes the EAP estimate and posterior variance. Plausible values are then generated from the respondent-specific distribution defined by these two posterior moments.

## Plausible values for `sim_a1`

The following code generates 10 plausible values per respondent from the
FARLR debiasing model fitted to `sim_a1`.

```{r farlr-pv}
PVs_debias <- Farlr_drawPVs(
  mmlcomp = mmlcomp_debias,
  npv = 8L,
  seed = 2026
)
# |=============================================================| 100%

PVs_debias$datPVs |>
  head() |>
  dplyr::mutate(dplyr::across(where(is.numeric), \(x) round(x, 3)))
# id  _farl1  _farl2  _farl3  _farl4  _farl5  _farl6  _farl7 _farl8
# 1	1	1.584	  0.856	  1.410	  1.308	  1.044	  0.204	  1.013	  0.883
# 2	2	-0.187	-0.446	-0.417	-0.559	-0.335	-0.336	-1.360	0.357
# 3	3	0.032	  -0.144	-0.595	0.065	  -0.385	-0.312	-0.854	0.407
# 4	4	-0.797	0.071	  -0.011	-0.792	-0.518	-0.014	-1.066	-0.742
# 5	5	0.099	  0.352	  0.287	  0.710	  0.464	  -0.175	0.457	  -0.146
# 6	6	-0.455	0.383	  -0.476	0.179	  -0.315	0.660	  0.354	  -0.129

head(PVs_debias$EAP_estimates)
# [1]  1.34700172 -0.23687530 -0.23971835 -0.81915496  0.20881138 0.04569881
```

<!-- BEGIN: paste sim_a1 plausible-value output here -->

```text
# Paste head(PVs_debias$datPVs) here.
# Paste head(PVs_debias$EAP_estimates) here.
```

<!-- END: paste sim_a1 plausible-value output here -->

The `datPVs` component contains one row per respondent, with `id` identifying
the respondent and `_farl1`, ..., `_farl10` containing the plausible values.
The `EAP_estimates` and `EAP_variance` components contain the posterior mean
and variance used to generate the plausible values.

## Plausible values for `sim_a2`

The same function can be used for the mixed 3PL/GPCM responses in `sim_a2`.
The item-specific response types and parameters stored in the fitted FARLR
object are used automatically when evaluating each respondent's likelihood.

```{r farlr-mixed-pv}
PVs_mixed <- Farlr_drawPVs(
  mmlcomp = mmlcomp_mixed,
  npv = 8L,
  seed = 2026
)
# |=================================================================================================================================| 100%

PVs_mixed$datPVs |>
  head() |>
  dplyr::mutate(dplyr::across(where(is.numeric), \(x) round(x, 3)))
#  id _farl1  _farl2  _farl3  _farl4  _farl5  _farl6  _farl7 _farl8
# 1	1	1.320	  0.657	  1.162	  1.069	  0.828	  0.062	  0.800	  0.682
# 2	2	0.369	  0.153	  0.177	  0.059	  0.246	  0.244	  -0.607	0.821
# 3	3	0.277	  0.130	  -0.245	0.304	  -0.070	-0.010	-0.461	0.589
# 4	4	-0.535	0.148	  0.082	  -0.532	-0.316	0.081	  -0.747	-0.492
# 5	5	-0.267	-0.051	-0.107	0.255	  0.044	  -0.502	0.039	  -0.477
# 6	6	-0.254	0.460	  -0.272	0.286	  -0.135	0.696	  0.435	  0.024

head(PVs_mixed$EAP_estimates)
# [1]  1.10437426  0.32693799  0.05039616 -0.55292495 -0.17377925  0.17274363
```

<!-- BEGIN: paste sim_a2 plausible-value output here -->

```text
# Paste head(PVs_mixed$datPVs) here.
# Paste head(PVs_mixed$EAP_estimates) here.
```

<!-- END: paste sim_a2 plausible-value output here -->


# DIRE Marginal Maximum Likelihood

The PCA-based latent regression commonly used in large-scale assessments
reduces high-dimensional background variables to a selected set of principal
components. In FARL, `Dire_mml()` implements this comparison through the DIRE
package. It can apply PCA to the original covariates or to non-main covariates
after residualizing them on the key predictors, then adds the retained PC
scores to the latent regression formula.

## Prepare the DIRE data

```{r dire-data}
library(Dire)

X <- as.matrix(sim_a1$X)
resp <- as.matrix(sim_a1$Y)
n <- nrow(X)
J <- ncol(resp)

colnames(X) <- paste0("X", seq_len(ncol(X)))
main_vars <- paste0("X", main)

subject <- factor(seq_len(n))
stuDat <- data.frame(subject = subject, X)

item_names <- paste0("item", seq_len(J))
stuItems <- data.frame(
  subject = rep(subject, times = J),
  key = factor(rep(item_names, each = n), levels = item_names),
  score = as.vector(resp)
)

parTab <- sim_a1$parTab[, c(
  "ItemID", "test", "subtest", "slope",
  "difficulty", "guessing", "D"
)]
parTab$ItemID <- item_names

testDat <- data.frame(
  test = "comp",
  subtest = "main",
  location = 0,
  scale = 1
)
```

## Fit the model

The `pca_type` argument chooses covariance or correlation PCA, and
`var_threshold` specifies the cumulative proportion of variance retained.

```{r dire-fit}
mmlcomp_dire <- Dire_mml(
  formula = reformulate(main_vars, response = "comp"),
  stuItems = stuItems,
  stuDat = stuDat,
  idVar = "subject",
  dichotParamTab = parTab,
  testScale = testDat,
  X = X,
  main_vars = main_vars,
  pca_type = "cov",
  use_residual = TRUE,
  var_threshold = 0.90
)

round(mmlcomp_dire$coefficients,3)
 # (Intercept)            X1            X2           X29           X15           X45           PC1           PC2           PC3 
 #       -1.041         0.396         0.326         0.287         0.289         0.785         0.087         0.114        -0.120 
 #          PC4           PC5           PC6           PC7           PC8           PC9          PC10          PC11          PC12 
 #        0.145         0.235        -0.177        -0.296         0.156        -0.301        -0.016        -0.036         0.149 
 #         PC13          PC14          PC15          PC16          PC17          PC18          PC19          PC20          PC21 
 #       -0.095         0.254         0.110         0.011        -0.063        -0.112        -0.101         0.033        -0.088 
 #         PC22          PC23          PC24          PC25          PC26          PC27          PC28          PC29          PC30 
 #       -0.011         0.057         0.002        -0.032        -0.159        -0.504         0.121         0.125         0.231 
 #         PC31          PC32          PC33 Population SD 
 #       -0.135         0.005         0.107         0.633 

mmlcomp_dire$pca_object$num_pcs
# 33
```

## Draw DIRE plausible values

```{r dire-pv}
PVs_dire <- Dire_drawPVs(
  x = mmlcomp_dire,
  npv = 10L,
  pvVariableNameSuffix = "_dire"
)$data

# DIRE may sort character IDs internally. Restore the original respondent order.
pv_order <- match(
  as.character(seq_len(n)),
  as.character(PVs_dire$id)
)

PVs_dire <- PVs_dire[pv_order, , drop = FALSE]
rownames(PVs_dire) <- NULL

PVs_dire |>
  head() |>
  dplyr::mutate(dplyr::across(where(is.numeric), \(x) round(x, 3)))

#   id  _dire1  _dire2  _dire3  _dire4  _dire5  _dire6  _dire7  _dire8
# 1	1	  1.084	  0.996	  1.635	  1.640	  2.162	  2.149	  1.046	  1.246	
# 2	2	  0.350	  -0.542	0.010	  -0.479	-0.131	0.538	  -0.193	0.388	
# 3	3	  0.678	  -0.582	-0.234	-0.562	-0.345	-0.389	-0.815	0.092	
# 4	4	  -1.138	-0.468	-1.738	0.330	  -0.119	-0.532	-1.378	-0.581	
# 5	5	  -0.441	0.605	  0.443	  0.206	  1.238	  0.394	  0.405	  0.010	
# 6	6	  -0.157	-0.527	-0.277	-0.599	0.083	  -0.173	-0.231	0.149	

```

<!-- BEGIN: paste DIRE plausible-value output here -->

```text
# Paste head(PVs_dire) here.
```

<!-- END: paste DIRE plausible-value output here -->

# Package Evaluation

The following short functions can be used to test the primary FARL workflows.
Each function fits a model and returns the plausible-value result.

## FARLR Debias test

```{r test-debias}
mml_test_debias <- function() {
  mmlcomp <- with(
    sim_a1,
    Farlr_mml(
      X,
      Y,
      parTab,
      method = "FARLR_Debias",
      main = c(1, 2, 15, 29, 45),
      K_hat = 2,
      seed = 2026
    )
  )

  PVs <- Farlr_drawPVs(
    mmlcomp = mmlcomp,
    npv = 10L,
    seed = 2026
  )

  return(PVs)
}
```

## FARLR EMM test

```{r test-emm}
mml_test_emm <- function() {
  mmlcomp <- with(
    sim_a1,
    Farlr_mml(
      X,
      Y,
      parTab,
      method = "FARLR_EMM",
      main = c(1, 2, 15, 29, 45),
      seed = 2026
    )
  )

  PVs <- Farlr_drawPVs(
    mmlcomp = mmlcomp,
    npv = 10L,
    seed = 2026
  )

  return(PVs)
}
```

## Mixed-item test

```{r test-mixed}
mml_test_mixed <- function() {
  mmlcomp <- with(
    sim_a2,
    Farlr_mml(
      X,
      Y,
      parTab,
      method = "FARLR_Debias",
      main = c(1, 2, 15, 29, 45),
      seed = 2026
    )
  )

  PVs <- Farlr_drawPVs(
    mmlcomp = mmlcomp,
    npv = 10L,
    seed = 2026
  )

  return(PVs)
}
```

# Notes

- FARLR is intended to improve compatibility with common secondary analyses;
  it does not guarantee congeniality in the strict statistical sense.
- The current FARLR estimators are designed for a unidimensional latent
  proficiency model.
- Rows of `X` and `Y` must correspond to the same respondents.
- Rows of `parTab` must follow the item-column order in `Y`.
- `main` uses numeric column indices from `X`.
- Set `seed` for reproducible FARLR estimation and plausible values.
- Set `K_hat` when the number of factors is known; otherwise parallel analysis
  is used.
- For long-running package vignettes, prebuild the document or keep the model
  chunks unevaluated during routine package checks.
